Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
comment on alpha effect

>>>>

It should be noted that as $\alpha$ increases, the likelihood of the labeled training data matters more and more,
and the score is positively influenced up to a point---as \alpha increases further, the labeled data
dominates the loss function, and the information from the unstructured model ceases to be used,
causing a slow decline in the score.
